---
title: "PPPR-Program"
author: "PPPR Team"
date: "2/4/2022"
output:
  html_document: 
    toc: yes
    toc_depth: 4
    toc_float: yes
    code_folding: hide
    theme: paper
  pdf_document: default
---

```{=html}
<style>
p.caption {
  font-size: 0.8em;
  text-align: center;
  font-weight: normal;
}
    caption {
      color: grey;
      font-size: 0.8em;
    }
@font-face{
  font-family: Helvetica; 
  src:url('Helvetica.ttf');
}
body{
  font-size: 11pt;
  font-family: Helvetica;
}
h1,h2,h3,h4,h5,h6{
  font-family: Helvetica;
  color: red;
}
td{
  font-size: 9pt;
  font-family: Helvetica;
}
th{
  font-size: 0.8em;
  font-family: Helvetica;
  color: black;
}
</style>
```

------------------------------------------------------------------------
```{r setup, include=FALSE}

knitr::opts_chunk$set(error = TRUE, echo = TRUE)
```

```{r loadSecrets}

## NOTE: You will need to create secrets.json, using the template
## to enter private credentials for interacting with the database

get_secrets <- function() {
  path <- "secrets/secrets.json"
  if (!file.exists(path)) {
    stop("Can't find secret file: '", path, "'")
  }
  
  jsonlite::read_json(path)
}
secrets <- get_secrets()

# database settings
dbname = secrets$db_name
host = secrets$db_host
port = secrets$db_port
username =  secrets$db_username
password = secrets$db_password
```

### Set Up

```{r library, message=FALSE, warning=FALSE, results='hide'}
library(vroom)
library(sf)
library(ggplot2)
library(ggmap)
library(kableExtra)
library(tidyverse)
library(data.table)
#remotes::install_github("CityOfPhiladelphia/rphl")
library(rphl)
library(lubridate)
library(furrr)
library(rgdal)

ll <- function(dat, proj4 = 4326){st_transform(dat, proj4)}

root.dir = "https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/DATA/"
source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

#windowsFonts(font = windowsFont('Helvetica'))

crs = 'EPSG:2272'

plotTheme <- function(base_size = 9, title_size = 10){
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = title_size, colour = "black", hjust = 0.5), 
    plot.subtitle = element_text( face = 'italic',
                                 size = base_size, colour = "black", hjust = 0.5),
    plot.caption = element_text( hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),
    panel.grid.major = element_line("grey80", size = 0.01),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=.5),
    strip.background = element_blank(),
    strip.text = element_text( size=9),
    axis.title = element_text( size=9),
    axis.text = element_text( size=7),
    axis.text.y = element_text( size=7),
    plot.background = element_blank(),
    legend.background = element_blank(),
    legend.title = element_text( colour = "black", face = "italic", size = 9),
    legend.text = element_text( colour = "black", face = "italic", size = 7),
    strip.text.x = element_text( size = 9),
    legend.key.size = unit(.5, 'line')
  )
}

mapTheme <- function(base_size = 9, title_size = 10){
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = title_size, colour = "black", hjust = 0.5), 
    plot.subtitle = element_text( face = 'italic',
                                 size = base_size, colour = "black", hjust = 0.5),
    plot.caption = element_text( hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(size=base_size),
    axis.title = element_text( size=9),
    axis.text = element_blank(),
    axis.text.y = element_blank(),
    plot.background = element_blank(),
    legend.background = element_blank(),
    legend.title = element_text( colour = "black", face = "italic", size = 9),
    legend.text = element_text( colour = "black", face = "italic", size = 7),
    strip.text.x = element_text(size=base_size),
    legend.key.size = unit(.5, 'line')
  )
}

palette5 <- c("#f9b294","#f2727f","#c06c86","#6d5c7e","#315d7f")
palette4 <- c("#f9b294","#f2727f","#c06c86","#6d5c7e")
palette2 <- c("#f9b294","#f2727f")
palette1_main <- "#F2727F"
palette1_assist <- '#F9B294'
```

#### Folder: OpenDataPhilly

**Relevant data of PPR finder**
```{r openDataPhilly_pprDistrict,fig.height = 5,message = FALSE, warning = FALSE, results='hide',out.width = '75%',fig.align = 'center',fig.width=8, fig.height=6}

philly <- st_read("https://opendata.arcgis.com/datasets/405ec3da942d4e20869d4e1449a2be48_0.geojson")

pprDistrict <- st_read('https://opendata.arcgis.com/datasets/0cdc4a1e86c6463b9600f9d9fca39875_0.geojson') %>%
  st_transform(crs)

base_map <- get_map(location = unname(st_bbox(ll(st_buffer(st_union(pprDistrict),11000)))),maptype = "terrian")

#ggmap(base_map) + 
  #geom_sf(data=ll(st_union(pprDistrict)),color="black",size=2,fill = "transparent",inherit.aes = FALSE)+
  #geom_sf(data=ll(pprDistrict),color=palette1_main,size=2,fill = "transparent",inherit.aes = FALSE)+
  #labs(title = "", 
     #  subtitle = "",
     #  x="",y="")+
  #mapTheme()

# ppr District Map with ID

ggplot(pprDistrict) + 
  geom_sf(aes(inherit.aes = FALSE), show.legend = FALSE) + 
  geom_sf_label(aes(label = DISTRICTID), label.padding = unit(1, "mm"))+
    labs(title = "0.1 PPR Districts Map", 
       subtitle = "",
       x="",y="")+
  mapTheme()

pprProperties <- st_read('https://opendata.arcgis.com/datasets/d52445160ab14380a673e5849203eb64_0.geojson')%>%
  st_transform(crs)

ggplot() + 
  geom_sf(data=pprProperties,color=palette1_main,fill = palette1_main)+
  geom_sf(data=st_union(pprDistrict),color="black",size=2,fill = "transparent")+
  geom_sf(data=pprDistrict,color="black",size=1,linetype ="dashed",fill = "transparent")+
  labs(title = "0.2 PPR Properties Map", 
       subtitle = "",
       x="",y="")+
  mapTheme()
```

#### Folder: FromPPR (skip)

#### PPR_Service_Areas_2021

"data/FromPPR/PPR_Service_Areas_2021/PPR_Service_Areas_2021.shp"

#### PPR-recreation-permits-2021

"data/FromPPR/PPR-recreation-permits-2021.csv"

```{r fromPPR-recreation-permits-2021, warning=FALSE, message=FALSE}
perimit2021 <- vroom("data/FromPPR/PPR-recreation-permits-2021.csv")
kable(head(perimit2021,3),align = 'c',caption = '<center>Table 7. Program information of PPR Recreation data <center/>')%>%
  kable_classic(full_width = F)%>%
  kable_styling(position = "center")%>% 
  scroll_box(width = "100%", height = "400px")
```

#### PPR-programs-attended-2021-with-schedules

"PPR-programs-attended-2021-with-schedules.csv"

```{r fromPPR-programs-attended-2021, warning=FALSE, message=FALSE}
program2021 <- vroom("data/FromPPR/PPR-programs-attended-2021-with-schedules.csv")

kable(head(program2021,3),align = 'c',caption = '<center>Table 8. Program information of PPR Programs data <center/>')%>%
  kable_classic(full_width = F)%>%
  kable_styling(position = "center")%>% 
  scroll_box(width = "100%", height = "400px")
```

#### Service_Area_Sites

"Service_Area_Sites.csv"

```{r from Service_Area_Sites}
propertyArea <- read.csv("data/FromPPR/Service_Area_Sites.csv")
```

#### tblFacility_to_PPR_Properties

"tblFacility_to_PPR_Properties.csv"

```{r from tblFacility_to_PPR_Properties}

facilityID <- read.csv("data/FromPPR/tblFacility_to_PPR_Properties.csv")
```

### Data Wrangling

#### Property data

```{r join property data}
# replace "and" with "&"
pprProperties <- pprProperties %>% 
  mutate(OFFICIAL_NAME = gsub("and", "&", pprProperties$OFFICIAL_NAME),
         PUBLIC_NAME = gsub("and", "&", pprProperties$PUBLIC_NAME))


# join method 1
property.join1 <- left_join(propertyArea, 
                          pprProperties %>% dplyr::select(ADDRESS_911, geometry), 
                          by=c("X911.Address"="ADDRESS_911"), left=FALSE) %>% 
  filter(!st_is_empty(geometry))

# join method 2
property.join2 <- left_join(propertyArea, 
                          pprProperties %>% dplyr::select(OFFICIAL_NAME, geometry), 
                          by=c("PPR.Site.Name"="OFFICIAL_NAME"), left=FALSE) %>% 
  filter(!st_is_empty(geometry))

# join method 3
property.join3 <- left_join(propertyArea, 
                          pprProperties %>% dplyr::select(PUBLIC_NAME, geometry), 
                          by=c("PPR.Site.Name"="PUBLIC_NAME"), left=FALSE) %>% 
  filter(!st_is_empty(geometry))

# combine 3 methods together
property <- rbind(property.join1,property.join2) %>% 
  rbind(property.join3,.) %>% 
  distinct()

x <- left_join(propertyArea, property, by="PPR.Site.Name") %>% 
  filter(st_is_empty(geometry))

```

#### Program data

```{r wrangle program data}
# define date 
program2021.clean <- program2021 %>% 
  mutate(AttendanceWeekDate = mdy(AttendanceWeekDate),
         DateFrom = mdy(DateFrom),
         DateTo = mdy(DateTo))

# create a df only containing records without program scheduel info
program2021.NA <- program2021.clean[is.na(program2021.clean$ProgramScheduleID),]

# filter by attendance date
program2021.clean <- program2021.clean %>% 
  filter(AttendanceWeekDate > DateFrom & AttendanceWeekDate < DateTo)

# original data is recorded by week, here we change it into being recorded by occurrence
program2021.clean <- separate(program2021.clean, Days,into= c("1","2","3","4","5","6","7"))

program2021.clean <- program2021.clean %>% 
  gather(colNames, weekday, 15:21) %>% 
  select(-colNames) %>% 
  na.omit(cols='weekday')

# create exact attendance date
program2021.clean <- program2021.clean %>% 
  mutate(AttendenceRealDate = case_when(
    weekday == "Monday" ~ AttendanceWeekDate,
    weekday == "Tuesday" ~ AttendanceWeekDate+1,
    weekday == "Wednesday" ~ AttendanceWeekDate+2,
    weekday == "Thursday" ~ AttendanceWeekDate+3,
    weekday == "Friday" ~ AttendanceWeekDate+4,
    weekday == "Saturday" ~ AttendanceWeekDate+5,
    weekday == "Sunday" ~ AttendanceWeekDate+6,
  ))

propertyParent <- pprProperties %>% 
  filter(NESTED=="N")

propertyKid <- pprProperties %>% 
  filter(NESTED=="Y")


```

#### Join program data

```{r join property and program data}
program2021.join <- left_join(program2021.clean, facilityID, by =c("FacilityID")) %>% 
  left_join(., pprProperties, by =c("PPR_Properties_ObjectID"="OBJECTID"))
```

### 2022/02/05 Existing Program Analysis

#### 1.1 Distribution of Facilities and Programs in Service Area 7

```{r, data wrangling, message = FALSE, warning = FALSE, results='hide'，fig.width=8, fig.height=6}

# Wrangle "program2021.join", and extract month attendance

Facility_2021 <- program2021.join %>%
  select(Facility,ActivityType,
         AttendanceWeekDate,
         RegisteredIndividualsCount,
         PPR_DISTRICT) %>%
  
  mutate(month = case_when(month(AttendanceWeekDate)==1 ~ "01_Jan",
                           month(AttendanceWeekDate)==2 ~ "02_Feb",
                           month(AttendanceWeekDate)==3 ~ "03_Mar",
                           month(AttendanceWeekDate)==4 ~ "04_Apr",
                           month(AttendanceWeekDate)==5 ~ "05_May",
                           month(AttendanceWeekDate)==6 ~ "06_Jun",
                           month(AttendanceWeekDate)==7 ~ "07_Jul",
                           month(AttendanceWeekDate)==8 ~ "08_Aug",
                           month(AttendanceWeekDate)==9 ~ "09_Sep",
                           month(AttendanceWeekDate)==10 ~ "10_Oct",
                           month(AttendanceWeekDate)==11 ~ "11_Nov",
                           month(AttendanceWeekDate)==12 ~ "12_Dec"))

# Remove duplicate variables 

Facility_2021 <- distinct(Facility_2021,.keep_all = FALSE)

# Facility in DISTRICT 7

Facility_7 <- Facility_2021 %>%
  filter(PPR_DISTRICT == 7)

MonthVisit_7 <- aggregate(Facility_7$RegisteredIndividualsCount, by=list(month=Facility_7$month,Facility=Facility_7$Facility, ActivityType=Facility_7$ActivityType ), sum)%>%
  mutate(VisitorCount = x)%>%
  select(-x)

#Facility & Activity Distribution in Service Area 7

ggplot(Facility_7, aes(x= Facility, fill = ActivityType)) + 
    geom_bar(position="stack")+
    labs(y = "Occurence", fill="Facility", title = "1.1 Facility & Activity Distribution in Service Area 7")+ 
    facet_grid(~PPR_DISTRICT)
```

1.2 Visitor Counts by Month & Activity in Service Area 7

```{r, data visulization in 7, message = FALSE, warning = FALSE, results='hide'，fig.width=8, fig.height=6}

# Visitor Counts by Month & Activity in Service Area 7

ggplot(MonthVisit_7, aes(x = month, y = VisitorCount, group = ActivityType, colour = ActivityType)) +
  geom_line() + geom_point() +
  labs(title = "1.2 Visitor Counts by Month in Service Area 7",
       x = "Month",
       y = "Visitor Counts")

```

2.1  Facility & Activity Distribution in Service Area 8

```{r,data wrangling in 8, message = FALSE, warning = FALSE, results='hide'，fig.width=8, fig.height=6}

# Facility in DISTRICT 8

Facility_8 <- Facility_2021 %>%
  filter(PPR_DISTRICT == 8)

MonthVisit_8 <- aggregate(Facility_8$RegisteredIndividualsCount, by = list(month = Facility_8$month,Facility = Facility_8$Facility, ActivityType = Facility_8$ActivityType ), sum)%>%
  mutate(VisitorCount = x)%>%
  select(-x)

#Facility & Activity Distribution in Service Area 7

ggplot(Facility_8, aes(x= Facility, fill = ActivityType)) + 
    geom_bar(position="stack")+
    labs(y = "Occurence", fill="Facility", title = "2.1 Facility & Activity Distribution in Service Area 8")+ 
    facet_grid(~PPR_DISTRICT) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

2.2 Visitor Counts by Month in Service Area 8

```{r, data visulization in 8, message = FALSE, warning = FALSE, results='hide'，fig.width=8, fig.height=6}

# Visitor Counts by Month & Activity in Service Area 8

ggplot(MonthVisit_8, aes(x = month, y = VisitorCount, group = ActivityType, colour = ActivityType)) +
  geom_line() + geom_point() +
  labs(title = "2.2 Visitor Counts by Month in Service Area 8",
       x = "Month",
       y = "Visitor Counts")

```

3.1 Distribution of Facilities and Programs in Service Area 9

```{r,data wrangling in 9, message = FALSE, warning = FALSE, results='hide'，fig.width=8, fig.height=6}

# Facility in DISTRICT 9

Facility_9 <- Facility_2021 %>%
  filter(PPR_DISTRICT == 9)

MonthVisit_9 <- aggregate(Facility_9$RegisteredIndividualsCount, by = list(month = Facility_9$month,Facility = Facility_9$Facility, ActivityType = Facility_9$ActivityType), sum)%>%
  mutate(VisitorCount = x)%>%
  select(-x)

#Facility & Activity Distribution in Service Area 7

ggplot(Facility_9, aes(x= Facility, fill = ActivityType)) + 
    geom_bar(position="stack")+
    labs(y = "Occurence", fill="Facility", title = "3.1 Facility & Activity Distribution in Service Area 9")+ 
    facet_grid(~PPR_DISTRICT) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

3.2 Visitor Counts by Month in Service Area 9

```{r, data visulization in 9, message = FALSE, warning = FALSE, results='hide'，fig.width=8, fig.height=6}

# Visitor Counts by Month & Activity in Service Area 9

ggplot(MonthVisit_9, aes(x = month, y = VisitorCount, group = ActivityType, colour = ActivityType)) +
  geom_line() + geom_point() +
  labs(title = "3.2 Visitor Counts by Month in Service Area 9",
       x = "Month",
       y = "Visitor Counts")

```

4.1 Distribution of Facilities and Programs in Other Service Areas (1-6 & 10)

```{r,data wrangling in other service Areas, message = FALSE, warning = FALSE, results='hide'，fig.width=12, fig.height=8}

# Facility in Other DISTRICTS


Facility_other <- mutate_at(Facility_2021, c('PPR_DISTRICT'), ~replace(., is.na(.), 0))


Facility_other <- Facility_other %>%
  filter(PPR_DISTRICT == 0)

MonthVisit_other <- aggregate(Facility_other$RegisteredIndividualsCount, by = list(month = Facility_other$month,Facility = Facility_other$Facility, ActivityType = Facility_other$ActivityType), sum)%>%
  mutate(VisitorCount = x)%>%
  select(-x)

#Facility & Activity Distribution in Service Area 7

ggplot(Facility_other, aes(x= Facility, fill = ActivityType)) + 
    geom_bar(position="stack")+
    labs(y = "Occurence", fill="Facility", title = "4.1 Facility & Activity Distribution in Other Service Areas")+ 
    facet_grid(~PPR_DISTRICT) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

